A Computational Perspective On Spatial Perspective Transformations: From Sensory Inference To Imagined Self-motion

### 2017-03-24 draft-manuscript.Rmd
converted to word and sent to Fred
restarted working on manuscript

lang              : "english"
class             : "man"
output            : papaja::apa6_word
# output            : papaja::apa6_pdf
---

@@

# Vestibular Cognition
Two tasks thought to constitute vestibular cognition are : SPT and imagined self-motion. We show that both processes are thought to involve a simulated rotation about the body's vertical (yaw) axis. Describe both processes and show figure. Both can be interpreted as mentally simulated rotations. We refer to both as simulation: in this case we show that the simulation consists of simulating a dynamical system using a generative model. Simulation can also be thought of as a kind of internal 'replay' [@Takac:2012jc] or working memory representation

>>>>

lang              : "english"
class             : "man"
# output            : papaja::apa6_word
output            : papaja::apa6_pdf
---

@@

# Vestibular Cognition
Two tasks thought to constitute vestibular cognition are : SPT and imagined self-motion. = = = = =  Describe both processes and show figure. Both can be interpreted as mentally simulated rotations. We refer to both as simulation: in this case we show that the simulation consists of simulating a dynamical system using a generative model. Simulation can also be thought of as a kind of internal 'replay' [@Takac:2012jc] or working memory representation

### 2017-03-24 manuscript.Rmd
restarted working on manuscript

>>>>

Note the the vestibular senspry input may be the result of a superposition of multiple generative source; the afferent signals, measuring head velocity, may be caused by a multitude of processes (active head turn, unintentional body sway, perturbative external forcec (wind), etc.). The brain must treat these resulting head movements differently; active head turn may be goal-directed, with the aim of directing the gaze toward a target. In this case, no compensatory action os desired in order to counteract the movement. This would be counterproductive. However, in order to maintian postural stability, the brain must compensate for all movement that is not gol-directed, i.e. does not occur as a result of "planned" active motion. These components may be separated either at the level of the outcome variable (sensory signal), or at the level of the latent state variables. The latter amounts ot a latent decomposition.

> Estimated velocity due to active/passive movement must be trated differently. Sensory signals due to active motion (re-afference) can be viewed as being cause by known explanatory variables, or as intervention effects.

> discuss @Sanders_2015 (artificial velcoity vector)
